---
title: "JiT Summary"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r processing, include=FALSE, warning=FALSE,message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(ggpubr)
theme_set(theme_pubr())

df <- read_excel("C:/Users/DavidMcCullough/Marzano Research/MZR - Share/10_REL/Task 6-Research/CE6.6_JiT/Data Entry/Analysis/Output/Kansas_data.xlsx")

vars <- names(df)

```


```{r Internet Access, echo=FALSE}
variable <- 5
```

```{r code for plots, include=FALSE}
#Overview
temp <- df %>% 
  filter(!is.na(get(vars[variable]))) %>% 
  group_by(get(vars[variable])) %>% 
  tally() %>% 
  mutate(percent = round((n/sum(n))*100,digits = 1))

names(temp)[1] <- vars[variable]
temp <- temp[temp[1] != 'NA',]

p1 <- ggplot(data = temp, aes(x=factor(get(vars[variable])),y=percent,fill=factor(get(vars[variable])))) + 
  geom_bar(stat = "identity", position = position_dodge(0.9)) +
  theme(axis.text.x = element_blank(),
        plot.caption = element_text(hjust = 0, 
                                    face= "italic"),
        plot.title = element_text(hjust = 0.5)) +
  labs(fill="Response:", 
       y="Percent", 
       x="", 
       caption="Figure 1: Percentage of school districts in Kansas indicating internet access options") + 
  ggtitle(tools::toTitleCase(vars[variable])) + 
  fill_palette("nejm")

t1 <- knitr::kable(spread(data = temp[,-2],key = get(vars[variable]),value = percent))

#Urban-rural
temp <- df %>% 
  filter(!is.na(get(vars[variable]))) %>% 
  group_by(`Urban-Centric Locale`, get(vars[variable])) %>% 
  tally() %>% 
  mutate(percent = round((n/sum(n))*100,digits = 1))

names(temp)[2] <- vars[variable]
temp <- temp[temp[2] != 'NA',]

p2 <- ggplot(data = temp, aes(x=factor(get(vars[variable])),y=percent,fill=factor(get(vars[variable])))) + 
  geom_bar(stat = "identity", position = position_dodge(0.9)) + 
  facet_grid(cols = vars(`Urban-Centric Locale`)) + 
  theme(axis.text.x = element_blank(),
        plot.caption = element_text(hjust = 0, 
                                    face= "italic"),
        plot.title = element_text(hjust = 0.5)) +
  labs(fill="Response:", 
       y="Percent", 
       x="", 
       caption="Figure 1: Percentage of school districts in Kansas indicating internet access options, by NCES locale designation") + 
  fill_palette("nejm")

p2a <- ggplot(data = temp, aes(x=`Urban-Centric Locale`,y=percent,fill=factor(get(vars[variable])))) + 
  geom_bar(position="fill", stat="identity") +
  theme(plot.caption = element_text(hjust = 0, 
                                    face= "italic"),
        plot.title = element_text(hjust = 0.5)) +
  labs(fill="Response:", 
       y="Percent", 
       x="", 
       caption="Figure 1: Percentage of school districts in Kansas indicating internet access options by \nNCES locale designation") + 
  fill_palette("nejm")+ 
  coord_flip() + guides(fill = guide_legend(reverse=TRUE))

t2 <- knitr::kable(spread(data = temp[,-3],key = get(vars[variable]),value = percent))

#Internet Connectivity
temp <- df %>% 
  filter(!is.na(get(vars[variable]))) %>% 
  group_by(`Internet Connectivity`, get(vars[variable])) %>% 
  tally() %>% 
  mutate(percent = round((n/sum(n))*100,digits = 1))

names(temp)[2] <- vars[variable]
temp <- temp[temp[2] != 'NA',]

p3 <- ggplot(data = temp, aes(x=factor(get(vars[variable])),y=percent,fill=factor(get(vars[variable])))) + 
  geom_bar(stat = "identity", position = position_dodge(0.9)) + 
  facet_grid(cols = vars(`Internet Connectivity`)) + 
  theme(axis.text.x = element_blank(),
        plot.caption = element_text(hjust = 0, 
                                    face= "italic"),
        plot.title = element_text(hjust = 0.5)) +
  labs(fill="Response:", 
       y="Percent", 
       x="", 
       caption="Figure 1: Percentage of school districts in Kansas indicating internet access options, by NCES locale designation") + 
  fill_palette("nejm")

p3a <- ggplot(data = temp, aes(x=`Internet Connectivity`,y=percent,fill=factor(get(vars[variable])))) + 
  geom_bar(position="fill", stat="identity") +
  theme(plot.caption = element_text(hjust = 0, 
                                    face= "italic"),
        plot.title = element_text(hjust = 0.5)) +
  labs(fill="Response:", 
       y="Percent", 
       x="", 
       caption="Figure 1: Percentage of school districts in Kansas indicating internet access options by \nNCES locale designation") + 
  fill_palette("nejm")+ 
  coord_flip() + guides(fill = guide_legend(reverse=TRUE))

t3 <- knitr::kable(spread(data = temp[,-3],key = get(vars[variable]),value = percent))

```


## `r vars[variable]`

`r vars[variable]` responses were coded as `r paste(unique(df[[variable]])[1:length(unique(df[[variable]])) - 1], sep=",", collapse = ", ")` and `r paste(unique(df[[variable]])[length(unique(df[[variable]]))], sep=",", collapse = ", ")`.

### Overview

The distribution of `r vars[variable]` for school districts was calculated by summing the number of districts that were coded in each response category, then dividing each category by the total number of responses. These were then multiplied by 100 to yield a percentage. 

#### Figure: Barchart of the Percentage of `r vars[variable]` responses:

```{r, fig.width = 9, fig.height = 4, out.width='100%', fig.align= "center", echo=FALSE, warning=FALSE,message=FALSE}
#Faceted bar chart
p1
#Stacked percentages
```


#### Distribution of `r vars[variable]` (percentage):

```{r, echo=FALSE,warning=FALSE,message=FALSE}
t1
```

### Urban-Rural Locale

The distribution of `r vars[variable]` responses by school districts was calculated for each NCES Urban-rural locale classification. Within a particular urban-rural classificiation, the percentage indicating each `r vars[variable]` response was calculated by dividing the number of districts that indicated that `r vars[variable]` response by the total number of districts within that urbal-rural classification.

#### Figure: Barchart of the Percentage of `r vars[variable]` responses by NCES Locale classification

```{r, fig.width = 9, fig.height = 4, out.width='100%', fig.align= "center", echo=FALSE, warning=FALSE,message=FALSE}
#Faceted bar chart
p2
#Stacked percentages
```

#### Distribution of `r vars[variable]` responses by NCES Locale classification (percentage):

```{r, echo=FALSE,warning=FALSE,message=FALSE}
t2
```

### Internet Connectivity

The distribution of `r vars[variable]` responses by school districts was calculated for each NCES Internet Connectivity classification. Within a particular Internet Connectivity classificiation, the percentage indicating each `r vars[variable]` response was calculated by dividing the number of districts that indicated that `r vars[variable]` response by the total number of districts within that Internet Connectivity classification.

#### Figure: Barchart of the Percentage of `r vars[variable]` by NCES Internet Connectivity

```{r, fig.width = 9, fig.height = 4, out.width='100%', fig.align= "center", echo=FALSE, warning=FALSE,message=FALSE}
#Faceted bar chart
p3

#Stacked percentages
```

#### Distribution of `r vars[variable]` responses by NCES Internet Connectivity (percentage):

```{r, echo=FALSE, warning=FALSE,message=FALSE}
t3
```